|

### 2022-06-22 docs/rmd/paper.Rmd
autogit

---
title: |
  Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression:
    A comparison of $\epsilon$-Lexicase Selection and Tournament Selection
date: "Date of Submission: `r Sys.Date()`"
output:
  word_document:
    reference_docx: "templates/template_ls.docx"
    fig_caption: yes
    number_sections: true
always_allow_html: true 
fontsize: 12pt
toc: yes
toc_depth: 4
bibliography: bib/bib/ref.bib
csl: bib/csl/harvard1.csl
include-before: '`\newpage{}`{=latex}'
---

```{r setup, include=FALSE}

library(kableExtra)
library(magrittr)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = "!H")

# Abstract

...

@@

# References

>>>>

---
title: |
  <center>Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression: </center>
  <center>
    <small>
    A comparison of $\epsilon$-Lexicase Selection and Tournament Selection
     </small> 
  </center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Research Project: Seminar Information Systems (03.996.3299)</center>
  <center>Research Area: Computational Intelligence</center>
  <center>Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  <center>Summerterm 2022</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  pdf_document:
    keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: settings.tex
fontsize: 12pt
#toc: yes
# toc_depth: 4
bibliography: bib/bib/ref.bib
csl: bib/csl/harvard1.csl
#include-before: '`\newpage{} `{=latex}'
include-before: '`\thispagestyle{empty} `{=latex}'
---

```{r setup, include=FALSE}
library(kableExtra)
library(magrittr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = "!H")
```

\tableofcontents
\thispagestyle{empty}
\newpage

@@

# I   References {.unnumbered #I}

::: {#refs}
:::
\newpage

# II  Statutory Declaration {.unnumbered #II}
